Prepare Data

### 2021-12-08 report/figures/table_descriptives.tex
add analyses

<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Variables </th>
   <th style="text-align:right;"> Mean Value </th>
   <th style="text-align:right;"> St. Dev </th>
   <th style="text-align:right;"> Min. Value </th>
   <th style="text-align:right;"> Max. Value </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Far Right Party ID </td>
   <td style="text-align:right;"> 0.10 </td>
   <td style="text-align:right;"> 0.30 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Employment </td>
   <td style="text-align:right;"> 4.18 </td>
   <td style="text-align:right;"> 3.85 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 11 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Income </td>
   <td style="text-align:right;"> 6.94 </td>
   <td style="text-align:right;"> 2.64 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 13 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Ethnic Conception </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> National Identity </td>
   <td style="text-align:right;"> 3.63 </td>
   <td style="text-align:right;"> 0.90 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Knowledge </td>
   <td style="text-align:right;"> 1.47 </td>
   <td style="text-align:right;"> 0.82 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 3 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 2 </td>
   <td style="text-align:right;"> 3.32 </td>
   <td style="text-align:right;"> 1.17 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 3 </td>
   <td style="text-align:right;"> 3.84 </td>
   <td style="text-align:right;"> 0.97 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 4 </td>
   <td style="text-align:right;"> 3.55 </td>
   <td style="text-align:right;"> 0.99 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Interest </td>
   <td style="text-align:right;"> 2.93 </td>
   <td style="text-align:right;"> 1.09 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ideology </td>
   <td style="text-align:right;"> 4.75 </td>
   <td style="text-align:right;"> 1.79 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
</tbody>
</table>

>>>>

<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Variables </th>
   <th style="text-align:right;"> Mean Value </th>
   <th style="text-align:right;"> St. Dev </th>
   <th style="text-align:right;"> Min. Value </th>
   <th style="text-align:right;"> Max. Value </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Far Right Party ID </td>
   <td style="text-align:right;"> 0.1 </td>
   <td style="text-align:right;"> 0.30 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Employment </td>
   <td style="text-align:right;"> 4.2 </td>
   <td style="text-align:right;"> 3.87 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 11 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Income </td>
   <td style="text-align:right;"> 6.9 </td>
   <td style="text-align:right;"> 2.64 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 13 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Ethnic Conception </td>
   <td style="text-align:right;"> 0.5 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> National Identity </td>
   <td style="text-align:right;"> 3.6 </td>
   <td style="text-align:right;"> 0.89 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Knowledge </td>
   <td style="text-align:right;"> 1.5 </td>
   <td style="text-align:right;"> 0.82 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 3 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: People, not politicians, 
 should make the most 
 important political decisions </td>
   <td style="text-align:right;"> 3.3 </td>
   <td style="text-align:right;"> 1.19 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: MPs should follow 
 the will of the people </td>
   <td style="text-align:right;"> 3.8 </td>
   <td style="text-align:right;"> 0.99 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Differences between elites and 
 the people are bigger than 
 differences between the people </td>
   <td style="text-align:right;"> 3.5 </td>
   <td style="text-align:right;"> 1.02 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Too much talk, no action </td>
   <td style="text-align:right;"> 4.0 </td>
   <td style="text-align:right;"> 1.01 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Compromise is selling out </td>
   <td style="text-align:right;"> 3.2 </td>
   <td style="text-align:right;"> 1.15 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Attitude towards Pluralism </td>
   <td style="text-align:right;"> 4.2 </td>
   <td style="text-align:right;"> 0.86 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Interest </td>
   <td style="text-align:right;"> 2.9 </td>
   <td style="text-align:right;"> 1.09 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ideology </td>
   <td style="text-align:right;"> 4.8 </td>
   <td style="text-align:right;"> 1.79 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
</tbody>
</table>

### 2021-12-08 src/data-processing/prep_data.Rmd
add Online Appendix
add analyses

```{r "get data from Qualtrics", results="hide"}
## Match data with RESPONDI quota questions
d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
source(here("src/data-processing/clean_data.R"))
```

## Save Data for Analysis
```{r "save data",eval=FALSE}
save(d, file = here("data/intermediate/cleaned_experiment.RData"))
```

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  mutate(HT4 = (HT4_1 + HT4_2 + HT4_3 + HT4_4)/4) %>%
  select(#`Gender` = D1,
         #`Age` = D2,
         #`Education` = D3,
         `Region`  = D9,
         `Birth-place` = D10,
         `Urbanness`  = D4,
         `Job`  = D7,
         `Income`  = D8,
         `Political Knowledge (1)`  = PT4,
         `Political Knowledge (2)`  = PT5,
         `Political Knowledge (3)`  = PT6,
         `Political Interest`  = PT7,
         `Ideology`  = PT8,
         `Exclusive National Identity` = HT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```

>>>>

```{r "get data from Qualtrics", results="hide"}
## Match data with RESPONDI quota questions
d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
                    verbose = TRUE, force_request = T,
                    label = FALSE, convert = FALSE)
source(here("src/data-processing/clean_data.R"))

dem <- read_delim(here("data/raw-private/14651 data matched final.csv"), 
                  delim = ";") %>%
  select(id = tic, D2 = age, D1 = gender, D3 = education)

d <- left_join(d, dem)
rm(dem)
```

## Save Data for Analysis
```{r "save data"}
save(d, file = here("data/intermediate/cleaned_experiment.RData"))
```

@@

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  mutate(HT4 = (HT4_1 + HT4_2 + HT4_3 + HT4_4)/4) %>%
  select(`Gender` = D1,
         `Age` = D2,
         `Education` = D3,
         `Region`  = D9,
         `Birth-place` = D10,
         `Urbanness`  = D4,
         `Job`  = D7,
         `Income`  = D8,
         `Political Knowledge (1)`  = PT4,
         `Political Knowledge (2)`  = PT5,
         `Political Knowledge (3)`  = PT6,
         `Political Interest`  = PT7,
         `Ideology`  = PT8,
         `Exclusive National Identity` = HT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```
